### 2017-10-24 Draft2/AsymptoticNotation.tex
Finish removing P-notation?
Take care of Section 3

I will use the $\TextTilde$ relation to analyze time complexity. It is defined as follows:

\begin{align*}
f(n) \TextTilde g(n) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
\end{align*}

@@

Notice that while $O(2n) = O(n)$, $2n \TextTildeNot n$. Thus, $\TextTilde$ makes it possible to distinguish between a function that uses $n$ space and one that uses $2n$ space. \HdrNote A consequence of this is that bases for logarithms cannot be omitted, like in big-O notation.

@@

A useful property $\TextTilde$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergesOverArithmetic}.

\begin{theorem}
\label{thm:MergesOverArithmeticAdd}
	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
	\begin{align*}
	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
		(\hat{f} + \hat{g}) \TextTilde (f + g)\\
		(\hat{f} - \hat{g}) \TextTilde (f - g)
	\end{cases}
	\end{align*}
\end{theorem}

\begin{theorem}
\label{thm:MergesOverArithmeticMultiply}
	$P$ merges over multiplication and division. That is, for functions $f$ and $g$,
	\begin{align*}
	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
	\hat{f}\hat{g} \TextTilde fg\\
	\hat{f} / \hat{g} \TextTilde f / g
	\end{cases}
	\end{align*}
\end{theorem}

Another nice property $\TextTilde$ and $O$ have in common is that lower-order terms are removed from consideration. For example, $n \TextTilde n + \log_2 n$. This is stated by the below theorem, which is proved in \ref{pf:RemovesLowerOrderTerms}.

\begin{theorem}
	If $\lim_{n \to \infty} \frac{g(n)}{f(n)} = 0$, then $f(n) + g(n) \TextTilde f(n)$.
\end{theorem}

>>>>

To analyze time complexity, I will use the $\sim$ relation. It is defined as follows:

\begin{align*}
f(n) \sim g(n) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
\end{align*}

@@

Notice that while $O(2n) = O(n)$, $2n \not\sim n$. Thus, $\sim$ makes it possible to distinguish between a function that uses $n$ space and one that uses $2n$ space. {\HdrNote} A consequence of this is that bases for logarithms cannot be omitted, like in big-O notation.

@@

A useful property $\sim$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergesOverArithmetic}.

\begin{theorem}
\label{thm:MergesOverArithmeticAdd}
	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
	\begin{align*}
	(\hat{f} \sim f) \land (\hat{g} \sim g) \rightarrow \begin{cases}
		(\hat{f} + \hat{g}) \sim (f + g)\\
		(\hat{f} - \hat{g}) \sim (f - g)
	\end{cases}
	\end{align*}
\end{theorem}

\begin{theorem}
\label{thm:MergesOverArithmeticMultiply}
	$P$ merges over multiplication and division. That is, for functions $f$ and $g$,
	\begin{align*}
	(\hat{f} \sim f) \land (\hat{g} \sim g) \rightarrow \begin{cases}
	\hat{f}\hat{g} \sim fg\\
	\hat{f} / \hat{g} \sim f / g
	\end{cases}
	\end{align*}
\end{theorem}

Another nice property $\sim$ and $O$ have in common is that lower-order terms are removed from consideration. For example, $n \sim (n + \log_2 n)$. This is stated by the below theorem, which is proved in \ref{pf:RemovesLowerOrderTerms}.

\begin{theorem}
\label{thm:RemovesLowerOrderTerms}
	If $\lim_{n \to \infty} g / f = 0$, then $f + g \sim f$.
\end{theorem}

Finally, $\sim$ is a transitive operator. That is,

\begin{theorem}
\label{thm:Transitivity}
	If $f \sim g$ and $g \sim h$, then $f \sim h$.
\end{theorem}

This property is used implicitly by proofs that chain multiple $\sim$s in the form $f \sim g \sim h$, then conclude that $f \sim h$. It is proved in \ref{pf:Transitivity}.
